Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-12 paper/structureScene.tex
update section VI

For \emph{ob-w}, the cross-bin histogram distance used is a variant of the earth mover's distance ($\EMD$), known as $\widehat{\EMD}$ and introduced in \cite{pele2008linear}. $\EMD$ computes the distance between two histograms by finding the minimal cost to be paid to transform one histogram into the other. An advantage of $\EMD$ is that it automatically aligns the histogram bins by using a ``ground distance'' which is the distance between the bin centers in the two histograms. In our case, the histograms are the cluster weights $w^u$ defined over the bins formed by cluster centroids $\mu^u$.

@@

\begin{equation*}
\sum\limits_{n,m}f_{nm} = \min\left( \sum\limits_{n} w_n^u ,\sum\limits_{m} w_m^v \right)
\end{equation*} \ja{Can we provide some interpretation for the different terms and constraints here?}
where $\lbrace f_{nm} \rbrace$ is the flow between the cluster weights $w_n^u$ and $w_m^v$, that is, the amount transported from the $n$th bin to ``supply the demand'' of the $m$th bin. We denote by $D^{uv}$ the ground distance, a matrix containing the pairwise distances between the centroid sets $\mu^u$ and $\mu^v$. $D^{uv}$ is computed from the kernel $K$:
\begin{equation*}
D^{uv}=1-K^{(uv)}
\end{equation*}
with $K^{(uv)}$ being the slice of $K$ containing the pairwise similarities between the centroids sets $\mu^u$ and $\mu^v$ of the scenes $s_u$ and $s_v$ respectively. As suggested in \cite{pele2009fast}, we set the tradeoff parameter $\alpha$ to $1$.

>>>>

For \emph{ob-w}, the cross-bin histogram distance used is a variant of the earth mover's distance ($\EMD$), known as $\widehat{\EMD}$ and introduced in \cite{pele2008linear}. $\EMD$ computes the distance between two histograms by finding the minimal cost to be paid to transform one histogram into the other. An advantage of $\EMD$ is that it automatically aligns the histogram bins by using a ``ground distance'' which is the distance between the bin centers in the two histograms. In our case, the histograms are the clusters weights $w^u$ defined over the bins formed by clusters centroids $\mu^u$.

@@

\begin{equation*}
\sum\limits_{n,m}f_{nm} = \min\left( \sum\limits_{n} w_n^u ,\sum\limits_{m} w_m^v \right)
\end{equation*} \ja{Can we provide some interpretation for the different terms and constraints here?}
where $\lbrace f_{nm} \rbrace$ is the flow between the cluster weights $w_n^u$ and $w_m^v$, that is, the amount transported from the $n$th bin to ``supply the demand'' of the $m$th bin. We denote by $D^{uv}$ the ground distance, a matrix containing the pairwise distances between the centroids sets $\mu^u$ and $\mu^v$. $D^{uv}$ is computed from the kernel $K$:
\begin{equation*}
D^{uv}=1-K^{(uv)}
\end{equation*}
with $K^{(uv)}$ being the slice of $K$ containing the pairwise similarities between the centroids sets $\mu^u$ and $\mu^v$ of the scenes $s_u$ and $s_v$ respectively. As suggested in \cite{pele2009fast}, we set the tradeoff parameter $\alpha$ to $1$.
